---
title: "Figure1"
author: "Devi Veytia"
date: "2023-12-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Figure description/overview

This figure shows the Distribution of research across OROs and its time evolution

Panel A: Line plot of # articles for each ORO branch and Ocean & climate research by year     
Panel B: Barplot of # articles for each ORO type, filled by % articles in IPCC report. Perhaps also label at the top of the bar the year of the inflexion point of the exponential relationship    

*Key messages:*
1. there is exponential increase in research effort / articles on OROs  
? comparator : total number of articles on climate & Ocean / WoS query)	🡪(Panel a)
 
2. Research effort on OROs is dominated by articles on Renewable energy (50%)  (Panel b). Comparator IPCC ref list – hypothesize there will be very few on renewable energy but much more on NbS

3. Contrasted trends in research effort for the different OROs types (Panel b). 



# Set up

```{r load libraries}
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(ggplot2)
```


```{r Get the latest version of sqlite database and connect}

sqliteDir <- here::here("data/sqlite-databases")
sqliteFiles <- dir(sqliteDir)
sqliteVersions <- as.numeric(gsub(".sqlite","",substring(sqliteFiles, regexpr("_v", sqliteFiles) + 2)))
latestVersion <- sqliteFiles[which.max(sqliteVersions)]
dbcon <- RSQLite::dbConnect(RSQLite::SQLite(), file.path(sqliteDir, latestVersion), create=FALSE)
```


```{r import common aesthetics}
factor_aes <- readxl::read_excel(here::here("R/factor_aesthetics.xlsx"))

```

# Panel A: Line plot of # articles for each ORO branch and Ocean & climate research by year

For each year, and for each branch, count the number of lower, mean and upper articles relevant for each branch
```{r Sum n articles per oro branch per year}
predRel <- tbl(dbcon, "pred_relevance") 
pred_oro_branch <- tbl(dbcon, "pred_oro_branch")
uniquerefs <- tbl(dbcon, "allrefs")

oro_branch_by_year <- pred_oro_branch %>%
  inner_join(predRel %>% select(analysis_id, relevance_mean), by = "analysis_id")%>%
  filter(0.5 <= relevance_mean) %>%
  inner_join(uniquerefs %>% select(analysis_id, year), by = "analysis_id") %>%
  group_by(year) %>%
  summarise(
    Mitigation_mean = sum(0.5 <= `oro_branch.Mitigation - mean_prediction`),
    Mitigation_lower = sum(0.5 <= `oro_branch.Mitigation - lower_pred`),
    Mitigation_upper = sum(0.5 <= `oro_branch.Mitigation - upper_pred`),
    Nature_mean = sum(0.5 <= `oro_branch.Nature - mean_prediction`),
    Nature_lower = sum(0.5 <= `oro_branch.Nature - lower_pred`),
    Nature_upper = sum(0.5 <= `oro_branch.Nature - upper_pred`),
    Societal_mean = sum(0.5 <= `oro_branch.Societal - mean_prediction`),
    Societal_lower = sum(0.5 <= `oro_branch.Societal - lower_pred`),
    Societal_upper = sum(0.5 <= `oro_branch.Societal - upper_pred`)
  ) %>% 
  collect()

# Melt and reformat so each line is a yearxbranch, and then columns for mean, lower and upper
variables <- c("Mitigation","Nature","Societal")

for(v in 1:length(variables)){
  sub <- oro_branch_by_year[,c(1,grep(variables[v], colnames(oro_branch_by_year)))]
  colnames(sub) <- gsub(paste0(variables[v],"_"),"", colnames(sub))
  # sub <- reshape2::melt(sub, id.vars = "year", variable.name = "prediction_boundary", 
  #                       value.name = "n_articles")
  sub$ORO_branch <- paste(variables[v])
  if(v==1){
    oro_branch_by_year_sums <- sub
  }else{
    oro_branch_by_year_sums <- rbind(oro_branch_by_year_sums, sub)
  }
}


# Factor and format
oro_branch_by_year_sums <- oro_branch_by_year_sums%>%
  na.omit() %>%
  mutate(year = as.Date(paste0(year, "-01-01")),
         ORO_branch = factor(ORO_branch, levels = variables))

varAES <- factor_aes[which(factor_aes$variable == "ORO_branch"),]
varAES <- varAES[order(varAES$order),]
oro_branch_by_year_sums$ORO_branch <- factor(
  oro_branch_by_year_sums$ORO_branch,
  levels = varAES$level, labels = varAES$label
)

summary(oro_branch_by_year_sums)


# use the max year to set the x limits
xmax = max(oro_branch_by_year_sums$year)
xmin = min(oro_branch_by_year_sums$year)
```

```{r get number of articles from citation indexed databases}

## Web of Science
wos_by_year <- read.delim2(
  here::here("data/external/ocean-and-climate-publications/WOS_ocean-and-climate_by-year_2023-11-21.txt"))

wos_by_year <- wos_by_year %>%
  rename(year = Publication.Years, n_articles = Record.Count)%>%
  select(year, n_articles)%>%
  mutate(year = as.Date(paste0(year, "-01-01"))) %>%
  filter(xmin <= year & year <= xmax) %>%
  na.omit()


## Scopus
scopus_by_year <- read.csv(
  here::here("data/external/ocean-and-climate-publications/SCOPUS_ocean-and-climate_by-year_2023-11-21.csv"))

scopus_by_year <- scopus_by_year %>%
  mutate(year = as.Date(paste0(year, "-01-01"))) %>%
  filter(xmin <= year & year <= xmax)%>%
  na.omit()


```

```{r PLOT PANEL A}


fig1_A_ggp <- ggplot()+
  geom_ribbon(data = oro_branch_by_year_sums, 
              aes(x=year, ymin = log(lower), ymax=log(upper), fill = ORO_branch), alpha = 0.5)+
  geom_line(data = oro_branch_by_year_sums, aes(x=year, y=log(mean), col=ORO_branch), linewidth = 1)+
  geom_line(data = wos_by_year, 
            aes(x=year, y=log(n_articles), linetype = "WOS"), col="black", linewidth = 1)+
  geom_line(data = scopus_by_year, 
            aes(x=year, y=log(n_articles), linetype = "Scopus"), col="black", linewidth = 1)+
  scale_color_manual(values = varAES$colour, 
                     name = "ORO branch")+
  scale_fill_manual(values = c(as.vector(branchPal)), guide = FALSE)+
  scale_linetype_manual(values = c("solid","dotted"), name = "Database")+
  labs(x="Year", y="log(N articles)")+
  scale_x_date(limits = c(as.Date("1980-01-01"),xmax))+
  scale_y_continuous(sec.axis = sec_axis(trans = exp, name = "N articles"),
                     breaks = seq(0,90000, by= 30000))+
  theme_classic()+
  theme(legend.position = "right")

fig1_A_ggp
```


# Panel B: Barplot of N articles for each ORO type, filled by % articles in IPCC report. Perhaps also label at the top of the bar the year of the inflexion point of the exponential relationship

```{r load predictions for ORO type}
predRel <- tbl(dbcon, "pred_relevance") 
predType <- tbl(dbcon, "pred_oro_type_long") 
uniquerefs <- tbl(dbcon, "allrefs")

oro_branch_by_year <- pred_oro_branch %>%
  inner_join(predRel %>% select(analysis_id, relevance_mean), by = "analysis_id")%>%
  filter(0.5 <= relevance_mean) %>%
  inner_join(uniquerefs %>% select(analysis_id, year), by = "analysis_id") %>%
```

```{r Sum number of relevant articles for each oro type and boundary}
#factor_aes <- readxl::read_excel(here::here("R/factor_aesthetics.xlsx"))

oroTypeSums <- predType %>%
  group_by(oro_type) %>%
  summarise(
    n_mean = sum(0.5 <= mean),
    n_lower = sum(0.5 <= lower),
    n_upper = sum(0.5 <= upper)
  ) %>%
  collect()



typeAES <- factor_aes[which(factor_aes$variable == "oro_type"),]
typeAES <- typeAES[order(typeAES$order),]
oroTypeSums$oro_type <- factor(
  oroTypeSums$oro_type, 
  levels = typeAES$level, labels = typeAES$label
)


branchAES <- factor_aes[which(factor_aes$variable == "ORO_branch"),]
typeAES <- merge(typeAES, branchAES[,c("label","colour")] %>%
                       rename(oro_branch = label), by = "colour")

oroTypeSums <- cbind(oroTypeSums, typeAES[,c("order","colour","oro_branch")])
```


```{r}
fig1_B_ggp <- ggplot(oroTypeSums, aes(x=order, y=n_mean, fill = oro_branch))+
  geom_col()+
  geom_errorbar(aes(ymin = n_lower, ymax = n_upper), width=.2)+
  geom_text(aes(label = n_mean), nudge_y = 1000, size=3, col="red")+ #nudge_x=0.2,
  scale_fill_manual(name = "ORO branch", 
                    values = as.vector(branchAES$colour[order(branchAES$order)]))+
  scale_x_discrete(limits = factor(oroTypeSums$order), 
                    labels = oroTypeSums$oro_type[order(oroTypeSums$order)])+
  #ylim(c(0, max(temp$n_upper)+2000))+
  labs(y="N articles")+
  theme(
    panel.background = element_rect(fill="white",colour = "black"),
    panel.grid.major = element_line(colour = "grey"),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title.x = element_blank()
  )
fig1_B_ggp
```



ggsave(here::here("figures/main/annual-trends.pdf"),plot=annualTrend_ggp,
       width = 7, height=4.5, units="in")





Still need to match to the IPCC database and calculate the % of retrieval




