---
title: "Figure4"
author: "Devi Veytia"
date: "2023-12-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Figure description/overview

This figures shows the distribution of ORO types across coastal and marine systems

3 panels 	
a). Infographic of coastal land & built waterfronts (?) / coastal ocean / open ocean 		
b). ORO types vs. CIDs per system
c). ORO types vs. ecosystem types for coastal ocean only

*Key messages:*
1. Shift of ORO types across systems : Coastal land w. Societal adapatation, Coastal ocean w. Renewable energy (& Conservation), Open Ocean w. Mitigation

2. Shift of ecosystem types across OROs: Mangroves for CO2 removal, Coral reef for Conservation / Adapt:Nature, Mangrove / Seagrass for Conservation Adapt:Humans. 

# Set up

```{r load libraries}
library(dplyr)
library(dbplyr)
library(R.utils)
library(RSQLite)
library(ggplot2)
library(cowplot)
```


```{r Get the latest version of sqlite database and connect}

sqliteDir <- here::here("data/sqlite-databases")
sqliteFiles <- dir(sqliteDir)
sqliteVersions <- as.numeric(gsub(".sqlite","",substring(sqliteFiles, regexpr("_v", sqliteFiles) + 2)))
latestVersion <- sqliteFiles[which.max(sqliteVersions)]
dbcon <- RSQLite::dbConnect(RSQLite::SQLite(), file.path(sqliteDir, latestVersion), create=FALSE)
```


```{r import common aesthetics}
factor_aes <- readxl::read_excel(here::here("R/factor_aesthetics.xlsx"))

```


# Panel A: Infographic of coastal land & built waterfronts (?) / coastal ocean / open ocean

```{r read in svg image of infographic created in inkscape}
## Read in the infographic of the marine systems
fig4_A_Img <- magick::image_read(here::here("figures/inkscape/marineSystems.svg"))

# Plot of the svg infographic 
fig4_A_ggp <- ggdraw()+draw_image(fig4_A_Img, scale = 1)

fig4_A_ggp
```

# Panel B: Heatmap of ORO types vs. CIDs per system



```{r read in data for the plot - use only mean predictions}

## Access relevant tables

predRel <- tbl(dbcon, "pred_relevance") %>%
  filter(0.5 <= relevance_mean) %>%
  select(analysis_id)

predType <- tbl(dbcon, "pred_oro_type_long") %>%
  filter(0.5 <= mean) %>%
  select(analysis_id, oro_branch, oro_type) 

predMarSys <- tbl(dbcon, "pred_marine_system") %>%
  select(analysis_id, 
         `marine_system.land - mean_prediction`,
         `marine_system.coastal ocean - mean_prediction`,
         `marine_system.open-ocean - mean_prediction`) %>% 
  rename(land = `marine_system.land - mean_prediction`,
         coastal_ocean = `marine_system.coastal ocean - mean_prediction`,
         open_ocean = `marine_system.open-ocean - mean_prediction`) %>%
  collect()%>%
  reshape2::melt(id.vars = c("analysis_id"), variable.name = "marine_system", value.name = 'mean') %>%
  filter(0.5 <= mean) %>%
  select(-c(mean))

predThreat <- tbl(dbcon, "pred_climate_threat") %>%
  select(analysis_id,
         `climate_threat.Temperature - mean_prediction`,
         `climate_threat.SLR - mean_prediction`,
         `climate_threat.Extreme_weather - mean_prediction`) %>%
  rename(Temperature = `climate_threat.Temperature - mean_prediction`,
         SLR = `climate_threat.SLR - mean_prediction`,
         Extreme_weather = `climate_threat.Extreme_weather - mean_prediction`) %>%
  collect() %>%
  reshape2::melt(id.vars = c("analysis_id"), variable.name = "climate_threat", value.name = 'mean') %>%
  filter(0.5 <= mean) %>%
  select(-c(mean))
  


## Data joining and calculations
# Format into data frame where each row is a publication (unique analysis_id)

# Include only articles that have a prediction for ORO type AND marine system
marSysTypeThreatDf <- predRel %>%
  inner_join(predType, by="analysis_id") %>%
  collect() %>%
  inner_join(predMarSys, by="analysis_id")

# predictions for climate threat can be optional, because NA value will be classified as 'other'
# so use left_join to add in threats
marSysTypeThreatDf <- marSysTypeThreatDf %>%
  left_join(predThreat, by="analysis_id")

# Tabulate counts for the intersection of the different factors
marSysTypeThreatSums <- marSysTypeThreatDf %>%
  group_by(oro_branch, oro_type, marine_system, climate_threat) %>%
  summarise(n_articles = n())



## Factoring variables for plotting

# retrieve aesthetics for relevant factoring variables
typeAES <- factor_aes[which(factor_aes$variable == "oro_type"),]
typeAES <- typeAES[order(typeAES$order),]
marSysAES <- factor_aes[which(factor_aes$variable == "marine_system"),]
marSysAES <- marSysAES[order(marSysAES$order),]
threatAES <- factor_aes[which(factor_aes$variable == "climate_threat"),]
threatAES <- threatAES[order(threatAES$order),]
threatAES$level[which(threatAES$level == "NA")] <- NA

# use aesthetics to factor variables
marSysTypeThreatSums <- marSysTypeThreatSums %>%
  mutate(
    oro_type = factor(oro_type, levels = typeAES$level, labels = typeAES$label),
    marine_system = factor(marine_system, levels = marSysAES$level, labels = marSysAES$label),
    climate_threat = factor(climate_threat, levels = threatAES$level, labels = threatAES$label, exclude = NULL)
  )

```

Plot panel B with the breaks based on quantile

```{r plot panel B breaks based on quantile}
nDat <- marSysTypeThreatSums
nDat$n_articles[which(nDat$climate_threat == "Unidentified")] <- NA
naDat <- marSysTypeThreatSums %>%
            filter(climate_threat == "Unidentified") %>%
            rename(na_articles = n_articles)

# function to scale breaks between 0-1 for inputting values in scale fill stepsn function
range01 <- function(x){(x-min(x))/(max(x)-min(x))} 

# get quantile for climate threat and unidentified datasets separately to get breaks
# because they will be plotted on two different colour scales
breaksFill <- quantile(marSysTypeThreatSums$n_articles[marSysTypeThreatSums$climate_threat != "Unidentified"], na.rm=T) # get the quantile values
breaksFill <- signif(breaksFill, digits = 2) # cap at 2 signif
breaksFill <- round((breaksFill/10))*10 # round to the nearest 10
breaksFill <- unique(breaksFill) # if two quantiles are the same value remove
breaksFill[1] <- 0 # set min to 0

breaksNA <- quantile(naDat$na_articles[marSysTypeThreatSums$climate_threat != "Unidentified"], na.rm=T)
breaksNA <- signif(breaksNA, digits = 2) 
breaksNA <- round((breaksNA/10))*10 
breaksNA <- unique(breaksNA)
breaksNA[1] <- 0

# Plot
fig4_B_quantile_ggp <- ggplot(nDat, aes(x = climate_threat, y=oro_type))+
  facet_grid(vars(marine_system))+
  # Fill for all articles
  geom_tile(aes(fill = n_articles))+
  scale_fill_binned(name = "N articles", 
               type = "viridis",
               breaks = breaksFill, nice.breaks = FALSE,
               labels = function(x) ifelse(1000 <= x, paste(x/1000, "k"), paste(x)),
               rescaler = scales::rescale,
               #values = range01(breaksFill),
               show.limits = TRUE, 
               limits = breaksFill[c(1, length(breaksFill))], 
               oob= scales::squish,
               na.value = "transparent",
               guide = guide_coloursteps(order = 1),
               position = "top")+ 
  
  # new fill scale for unidentified climate threats
  new_scale_fill()+
  geom_tile(data = naDat,
            aes(fill = na_articles))+
  scale_fill_stepsn(name = "N unidentified", 
                    breaks=breaksNA,
                    labels = function(x) ifelse(1000 <= x, paste(x/1000, "k"), paste(x)),
                    colours = gray.colors(length(breaksNA)),
                    values = range01(breaksNA),
                    show.limits = TRUE, limits = breaksNA[c(1, length(breaksNA))],
                    na.value = "transparent", 
                    guide = guide_coloursteps(order = 2),
                    position = "bottom")+
  
  # other aesthetics
  labs(x="Climate impact driver")+ 
  scale_y_discrete(limits = rev)+

  theme_bw()+
  theme(
    axis.text.x = element_text(angle = 30, hjust=1, vjust=1),
    legend.position = "left",
    axis.title.y = element_blank(),
    legend.key.width = unit(1, 'cm'),
    legend.key.height = unit(0.4, 'cm')
  )

fig4_B_quantile_ggp
```


plot panel B breaks based on even breaks - does not look great because data are not distributed evenly
```{r plot panel B breaks based on even breaks - does not look great, eval=FALSE}
nDat <- marSysTypeThreatSums
nDat$n_articles[which(nDat$climate_threat == "Unidentified")] <- NA
naDat <- marSysTypeThreatSums %>%
            filter(climate_threat == "Unidentified") %>%
            rename(na_articles = n_articles)



# get even but pretty breaks for each of the datasets
breaksFill <- seq(0, max(marSysTypeThreatSums$n_articles[marSysTypeThreatSums$climate_threat != "Unidentified"], na.rm=T), length.out = 5) # get the quantile values
breaksFill <- signif(breaksFill, digits = 2) # cap at 2 signif
breaksFill <- round((breaksFill/500))*500 # round to the nearest 100
breaksFill <- unique(breaksFill) # if two quantiles are the same value remove

breaksNA <- seq(0, max(naDat$na_articles[marSysTypeThreatSums$climate_threat != "Unidentified"], na.rm=T), length.out = 5)
breaksNA <- signif(breaksNA, digits = 2) 
breaksNA <- round((breaksNA/5000))*5000
breaksNA <- unique(breaksNA)


## Plot
fig4_B_even_ggp <- ggplot(nDat, aes(x = climate_threat, y=oro_type))+
  facet_grid(vars(marine_system))+
  # Fill for all articles
  geom_tile(aes(fill = n_articles))+
  # scale_fill_stepsn(name = "N articles", 
  #                   n.breaks = n_breaksFill, nice.breaks = TRUE,
  #                   labels = function(x) ifelse(1000 <= x, paste(signif(x/1000, digits=2), "k"), paste(x)),
  #                   colors = viridis::viridis(n_breaksFill),
  #                   values = seq(0,1, by=0.25),
  #                   show.limits = TRUE, limits = c(0, max(nDat$n_articles, na.rm = T)),
  #                   na.value = "transparent")+ 
  scale_fill_binned(name = "N articles", 
               type = "viridis",
               breaks = breaksFill, nice.breaks = FALSE,
               labels = function(x) ifelse(1000 <= x, paste(x/1000, "k"), paste(x)),
               rescaler = scales::rescale,
               #values = range01(breaksFill),
               show.limits = TRUE, 
               limits = breaksFill[c(1, length(breaksFill))], 
               oob= scales::squish,
               na.value = "transparent",
               guide = guide_coloursteps(order = 1),
               position = "top")+ 
  
  # new fill scale
  new_scale_fill()+
  geom_tile(data = naDat,
            aes(fill = na_articles))+
  scale_fill_stepsn(name = "N unidentified", 
                    breaks=breaksNA,
                    labels = function(x) ifelse(1000 <= x, paste(x/1000, "k"), paste(x)),
                    colours = gray.colors(length(breaksNA)),
                    values = range01(breaksNA),
                    show.limits = TRUE, limits = breaksNA[c(1, length(breaksNA))],
                    na.value = "transparent", 
                    guide = guide_coloursteps(order = 2),
                    position = "bottom")+
  
  # other aesthetics
  labs(x="Climate impact driver")+ 
  
  scale_y_discrete(limits = rev)+
  #coord_flip()+
  theme_bw()+
  theme(
    axis.text.x = element_text(angle = 30, hjust=1, vjust=1),
    legend.position = "left",
    axis.title.y = element_blank(),
    legend.key.width = unit(1, 'cm'),
    legend.key.height = unit(0.4, 'cm')
  )

fig4_B_even_ggp
```

I feel like because the scales are so different between the panels, I will have to normalize by the number of articles in each oro type? Therfore to get 100%, need to sum up the values for that row across all the panels.

```{r plot panel B normalizing by oro type ie by row to make a percentage}
paneltotals <- marSysTypeThreatSums %>%
  group_by(oro_type) %>%
  summarise(total = sum(n_articles))

marSysTypeThreatSumsNorm <- marSysTypeThreatSums %>%
  left_join(paneltotals) %>%
  mutate(percent_articles = n_articles/total*100)

nDat <- marSysTypeThreatSumsNorm
nDat$percent_articles[which(nDat$climate_threat == "Unidentified")] <- NA
naDat <- marSysTypeThreatSumsNorm %>%
            filter(climate_threat == "Unidentified") %>%
            rename(na_articles = percent_articles)


# get even but pretty breaks for each of the datasets
breaksFill <- seq(0, max(marSysTypeThreatSumsNorm$percent_articles[marSysTypeThreatSumsNorm$climate_threat != "Unidentified"], na.rm=T), length.out = 10) # sequence even values across range
breaksFill <- signif(breaksFill, digits = 2) # cap at 2 signif
breaksFill <- round((breaksFill/5))*5 # round 
breaksFill <- unique(breaksFill) # if two quantiles are the same value remove

breaksNA <- seq(0, max(naDat$na_articles[marSysTypeThreatSums$climate_threat != "Unidentified"], na.rm=T), length.out = 5)
breaksNA <- signif(breaksNA, digits = 2) 
breaksNA <- round((breaksNA/5))*5
breaksNA <- unique(breaksNA)


## plot
fig4_B_percent_ggp <- ggplot(nDat, aes(x = climate_threat, y=oro_type))+
  facet_grid(vars(marine_system))+
  # Fill for all articles
  geom_tile(aes(fill = percent_articles))+
  # scale_fill_stepsn(name = "% articles", 
  #                   n.breaks = n_breaksFill, nice.breaks = TRUE,
  #                   labels = function(x){paste(x,"%")},
  #                   colors = viridis::viridis(n_breaksFill),
  #                   show.limits = TRUE, limits = c(0, max(nDat$percent_articles, na.rm = T)),
  #                   na.value = "transparent")+ 
  scale_fill_binned(name = "% articles", 
               type = "viridis",
               breaks = breaksFill, nice.breaks = FALSE,
               labels = function(x) ifelse(1000 <= x, paste(x/1000, "k"), paste(x)),
               rescaler = scales::rescale,
               #values = range01(breaksFill),
               show.limits = TRUE, 
               limits = breaksFill[c(1, length(breaksFill))], 
               oob= scales::squish,
               na.value = "transparent",
               guide = guide_coloursteps(order = 1, barwidth = unit(4, 'cm')), 
               position = "top")+ 
  
  # new fill scale
  new_scale_fill()+
  geom_tile(data = naDat,
            aes(fill = na_articles))+
  scale_fill_stepsn(name = "% unidentified", 
                    breaks=breaksNA,
                    labels = function(x) ifelse(1000 <= x, paste(x/1000, "k"), paste(x)),
                    colours = gray.colors(length(breaksNA)),
                    values = range01(breaksNA),
                    show.limits = TRUE, limits = breaksNA[c(1, length(breaksNA))],
                    na.value = "transparent", 
                    guide = guide_coloursteps(order = 2, barwidth = unit(3, 'cm')),
                    position = "bottom")+
  
  # other aesthetics
  labs(x="Climate impact driver")+ 
  
  #scale_y_discrete(limits = rev)+
  #coord_flip()+
  theme_bw()+
  theme(
    axis.text.x = element_text(angle = 30, hjust=1, vjust=1),
    legend.position = "top",
    axis.title.y = element_blank(),
    #legend.key.width = unit(0.4, 'cm'),
    legend.key.height = unit(0.2, 'cm'),
    legend.box = "vertical"
  )

fig4_B_percent_ggp
```


Still loses the idea of the gradient of changes in oro types across marine systems, so keep with the stacked bar plot? Include code here just in case
```{r old stacked bar plot version}
fig4_B_barplot_ggp <- ggplot(marSysTypeThreatSums, aes(y = oro_type, x=n_articles, fill = climate_threat))+
  facet_wrap(vars(marine_system), ncol=1, scales = "free")+
  geom_col(position = "stack")+
  labs(fill = "Climate impact\ndriver", x = "N articles")+ 
  # colour palette derived from the IBM design library colour blind safe palette
  # https://davidmathlogic.com/colorblind/#%23648FFF-%23785EF0-%23DC267F-%23FE6100-%23FFB000-%235E5C5E
  scale_fill_manual(values = threatAES$colour, breaks = threatAES$label, na.value = "transparent")+ 
  scale_y_discrete(limits = rev)+
  theme_bw()+
  theme(
    #axis.text.x = element_text(angle = 45, hjust=1, vjust=1)
    legend.position = "left",
    axis.title.y = element_blank()
  )

fig4_B_barplot_ggp
```


# Panel C: Heatmap of ORO types vs. ecosystem types and outcome for coastal ocean only

```{r get phylopics for ecosystem type}
pics <- dir(here::here("figures/phylopics/"))

# get mangrove
if(!("mangrove.svg" %in% pics)){
  mangrove_uuid <- rphylopic::get_uuid(name = "Rhizophora mangle", n=5)
  mangrove_img <- rphylopic::pick_phylopic(name = "Rhizophora mangle", n = 1)
  mangrove_img <- rphylopic::get_phylopic("bacc6a59-80d2-461c-92d4-83cabc91cc39")
  rphylopic::save_phylopic(img=mangrove_img,
                path = here::here("figures/phylopics/mangrove.svg"))
}


# Get coral
if(!("coral.svg" %in% pics)){
  coral_img <- rphylopic::get_phylopic("32eeaa29-2e90-40b5-92fb-eb8d7fcab9ab")
  rphylopic::save_phylopic(img = coral_img,
              path = here::here("figures/phylopics/coral.svg"))
}


# Get macroalgae
if(!("macroalgae.svg" %in% pics)){
  macro_img <- rphylopic::get_phylopic("9acf11fa-89dd-4a56-b3da-8665c406c6f5")
  rphylopic::save_phylopic(img = macro_img,
              path = here::here("figures/phylopics/macroalgae.svg"))
}


# get seagrass -- for some reason I had to download this directly from the website
#seagrass_img <- rphylopic::get_phylopic("2534e10f-ea8e-436e-a8c8-13ac045eb867")
#rphylopic::save_phylopic(img = seagrass_img,
#              path = here::here("figures/phylopics/seagrass.svg"))


library(magick)
marsh_ras <- as.raster(image_fill(image_read(here::here("figures/phylopics/saltmarsh.jpg")),'none'))
mangrove_ras <- as.raster(image_fill(image_read_svg(here::here("figures/phylopics/mangrove.svg")),'none'))
coral_ras <- as.raster(image_fill(image_read_svg(here::here("figures/phylopics/coral.svg")),'none'))
macro_ras <- as.raster(image_fill(image_read_svg(here::here("figures/phylopics/macroalgae.svg")),'none'))
seagrass_ras <- as.raster(image_fill(image_read_svg(here::here("figures/phylopics/seagrass.svg")),'none'))

```



```{r Changing salt marsh prediction threshold}
## Access relevant tables
predMarSys <- tbl(dbcon, "pred_marine_system") %>%
  select(analysis_id, 
         `marine_system.land - mean_prediction`,
         `marine_system.coastal ocean - mean_prediction`,
         `marine_system.open-ocean - mean_prediction`) %>% 
  rename(land = `marine_system.land - mean_prediction`,
         coastal_ocean = `marine_system.coastal ocean - mean_prediction`,
         open_ocean = `marine_system.open-ocean - mean_prediction`) %>%
  collect()%>%
  reshape2::melt(id.vars = c("analysis_id"), variable.name = "marine_system", value.name = 'mean') %>%
  filter(0.5 <= mean) %>%
  select(-c(mean))

saltMarshDf <- tbl(dbcon, "pred_ecosystem_type") %>%
  select(analysis_id,`ecosystem_type.Salt_marsh - mean_prediction`, 
         `ecosystem_type.Salt_marsh - upper_pred`) %>%
  rename(mean = `ecosystem_type.Salt_marsh - mean_prediction`,
         upper = `ecosystem_type.Salt_marsh - upper_pred`) %>%
  collect() %>%
  reshape2::melt(id.vars = "analysis_id", variable.name = "Prediction_boundary", value.name = "Prediction")

# Aesthetics for plotting
marSysAES <- factor_aes[which(factor_aes$variable == "marine_system"),]
marSysAES <- marSysAES[order(marSysAES$order),]



## Plot supplementary figure
saltMarshPredictions_ggp <- ggplot(saltMarshDf, aes(x=Prediction, fill = Prediction_boundary))+
  geom_histogram(alpha = 0.25, col = "black")+
  #geom_vline(xintercept = quantile(saltMarshDf$Prediction[saltMarshDf$Prediction_boundary == "upper"], probs=0.5)) +
  #annotation_raster(marsh_ras, 0.6, 0.9, 29000, 45000)+
  labs(y = "N articles", x = "Prediction", fill = "Prediction boundary"
    #caption = paste("Vertical line at 50% quantile for upper prediction =",
    #              signif(quantile(saltMarshDf$Prediction[saltMarshDf$Prediction_boundary == "upper"],
    #                              probs=0.5), digits=2))
    )+
  theme_classic()+
  theme(
    legend.position = "bottom"
  )



saltMarshMarSys_ggp <- saltMarshDf %>%
  filter(Prediction_boundary == "upper" & 
           0.5 <= Prediction) %>%
  left_join(predMarSys, by="analysis_id") %>% 
  mutate(marine_system = factor(marine_system, levels = marSysAES$level, marSysAES$label, exclude=FALSE)) %>%
  ggplot(aes(x=marine_system)) +
  geom_bar()+
  annotation_raster(marsh_ras, 3, 4.5, 25000, 40000)+
  labs(y="N articles", x="Marine system"#,
       #caption = "Using a threshold of 0.4 for relevance"
       )+
  theme_classic()+
  theme(
    axis.text.x = element_text(angle=45, vjust=1, hjust=1)
  )

## Save figure
pdf(here::here("figures/supplemental/saltMarshPredictionsHistogramAndMarineSystem.pdf"),
    width = 7, height=4.5)
egg::ggarrange(saltMarshPredictions_ggp, saltMarshMarSys_ggp,
          nrow=1, ncol=2, newpage = FALSE, labels = c("a.","b."))
dev.off()

```


Notes for changes in analysis - No predictions for salt marsh at mean prediction b/c low recall so use upper prediction limit instead. Choose value a little less than the median so that I can cut the distribution at the mode


```{r read in data for the plot}

## Access relevant tables
predRel <- tbl(dbcon, "pred_relevance") %>%
  filter(0.5 <= relevance_mean) %>%
  select(analysis_id)

predType <- tbl(dbcon, "pred_oro_type_long") %>%
  filter(0.5 <= mean) %>%
  select(analysis_id, oro_branch, oro_type) 

predMarSys <- tbl(dbcon, "pred_marine_system") %>%
  select(analysis_id, 
         `marine_system.land - mean_prediction`,
         `marine_system.coastal ocean - mean_prediction`,
         `marine_system.open-ocean - mean_prediction`) %>% 
  rename(land = `marine_system.land - mean_prediction`,
         coastal_ocean = `marine_system.coastal ocean - mean_prediction`,
         open_ocean = `marine_system.open-ocean - mean_prediction`) %>%
  collect()%>%
  reshape2::melt(id.vars = c("analysis_id"), variable.name = "marine_system", value.name = 'mean') %>%
  filter(0.5 <= mean) %>%
  select(-c(mean))

# NB here I change the filtering so salt marsh is included if 0.4 <= upper pred 
predEcoType <- tbl(dbcon, "pred_ecosystem_type") %>%
  select(analysis_id,
         `ecosystem_type.Salt_marsh - upper_pred`, ## ** `ecosystem_type.Salt_marsh - mean_prediction`
         `ecosystem_type.Mangrove - mean_prediction`,
         `ecosystem_type.Coral_reef - mean_prediction`,
         `ecosystem_type.Seagrass - mean_prediction`) %>%
  rename(Salt_marsh = `ecosystem_type.Salt_marsh - upper_pred`,
         Mangrove = `ecosystem_type.Mangrove - mean_prediction`,
         Coral_reef = `ecosystem_type.Coral_reef - mean_prediction`,
         Seagrass = `ecosystem_type.Seagrass - mean_prediction`) %>%
  collect() %>%
  reshape2::melt(id.vars = c("analysis_id"), variable.name = "ecosystem_type", value.name = 'prediction') %>%
  #filter(0.5 <= mean) %>%
  mutate(relevant = ifelse((ecosystem_type == "Salt_marsh" & 0.5 <= prediction) |
                             (ecosystem_type != "Salt_marsh" & 0.5 <= prediction), 1,0)) %>%
  filter(relevant == 1) %>%
  select(-c(prediction, relevant))

# Outcomes
predMit <- tbl(dbcon, "pred_climate_mitigation") %>%
  select(analysis_id, `0 - relevance - mean_prediction`) %>%
  rename(climate_mitigation = `0 - relevance - mean_prediction`) %>%
  #filter(0.5 <= climate_mitigation) %>%
  collect()

predAdapt <- tbl(dbcon, "pred_adapt_to_threat") %>%
  select(analysis_id,
         `adapt_to_threat.Human - mean_prediction`,
         `adapt_to_threat.Natural - mean_prediction`) %>%
  rename(Human = `adapt_to_threat.Human - mean_prediction`,
         Natural = `adapt_to_threat.Natural - mean_prediction`) %>%
  collect() 
  #reshape2::melt(id.vars = c("analysis_id"), variable.name = "adapt_to_threat", value.name = 'mean') %>%
  #filter(0.5 <= mean) 



## Retrieve aesthetics for relevant factoring variables
typeAES <- factor_aes[which(factor_aes$variable == "oro_type"),]
typeAES <- typeAES[order(typeAES$order),]
ecoTypeAES <- factor_aes[which(factor_aes$variable == "ecosystem_type"),]
ecoTypeAES <- ecoTypeAES[order(ecoTypeAES$order),]
adaptAES <- factor_aes[which(factor_aes$variable == "adapt_to_threat"),]
adaptAES <- adaptAES[order(adaptAES$order),]
```


Why are there a high number of coral reef papers and marine renewable energy predicted?
```{r Investigate the ecosystem x outcome for MRE}
MRE_Df <- predRel %>%
  inner_join(predType, by="analysis_id") %>%
  filter(oro_type == "Marine renewable energy" ) %>%
  collect() %>%
  inner_join(predMarSys, by="analysis_id") %>%
  #filter(marine_system == "coastal_ocean") %>%
  inner_join(predEcoType, by="analysis_id") %>%
  # Use left_join to add outcomes
  left_join(predMit, by="analysis_id") %>%
  left_join(predAdapt, by="analysis_id") %>%
  reshape2::melt(measure.vars = c("climate_mitigation","Human","Natural"), variable.name = "Outcome",
                 value.name = "Prediction") %>% 
  group_by(marine_system, ecosystem_type, Outcome) %>%
  summarise(n_articles = sum(0.5 <= Prediction))

MRE_ggp <- ggplot(MRE_Df, aes(x=ecosystem_type, y=Outcome, fill=n_articles))+
  facet_wrap(vars(marine_system))+
  geom_tile()

MRE_ggp
```



```{r Format dataframes and calculate sums for heatmaps}
## Data joining

# Format into data frame where each row is a publication (unique analysis_id)

# Include only articles that have a prediction for ORO type AND coastal marine system and ecosystem type
coastEcoTypeDf <- predRel %>%
  inner_join(predType, by="analysis_id") %>%
  collect() %>%
  inner_join(predMarSys, by="analysis_id") %>%
  filter(marine_system == "coastal_ocean") %>%
  inner_join(predEcoType, by="analysis_id")

# Use left_join to add outcomes
coastEcoTypeDf <- coastEcoTypeDf %>%
  left_join(predMit, by="analysis_id") %>%
  left_join(predAdapt, by="analysis_id")


# coastEcoTypeDf %>%
#   group_by(oro_type, ecosystem_type) %>%
#   summarise(climate_mitigation = sum(0.5 <= climate_mitigation))
# ggplot(
#          , aes(x=ecosystem_type, y=climate_mitigation))

## Factoring variables for plotting

# use aesthetics to factor variables
coastEcoTypeDf <- coastEcoTypeDf %>%
  mutate(
    oro_type = factor(oro_type, levels = typeAES$level, labels = typeAES$label),
    ecosystem_type = factor(ecosystem_type, levels = ecoTypeAES$level, labels = ecoTypeAES$label)
  )



# Tabulate counts for the intersection of the different factors
library(tidyr)
mitigationSums <- coastEcoTypeDf %>%
  group_by(oro_branch, oro_type, ecosystem_type) %>%
  summarise(n_articles = sum(0.5 <= climate_mitigation)) %>% #, na.rm=TRUE
  complete(ecosystem_type, fill = list(n_articles = 0))

adaptationSums <- coastEcoTypeDf %>%
  group_by(oro_branch, oro_type, ecosystem_type) %>%
  summarise(Human = sum(0.5 <= Human),
            Natural = sum(0.5 <= Natural)) %>%
  reshape2::melt(measure.vars = c("Human","Natural"), 
                 variable.name = "adapt_to_threat", value.name = "n_articles") %>%
  mutate(adapt_to_threat = factor(adapt_to_threat, levels = adaptAES$level, labels = adaptAES$label),
         n_articles = ifelse(is.na(n_articles),0, n_articles))


# Normalise by number of articles per ORO to get a percent

# calculate number of unique articles per oro type
# divide sums by these totals to get a percent of all coastal ecosystems
oroTotalsDF <- coastEcoTypeDf %>%
  filter(0.5 <= climate_mitigation |
           0.5 <= Human | 0.5 <= Natural) %>%
  group_by(oro_type) %>%
  summarise(total_coastEco = n_distinct(analysis_id))

mitigationSums <- mitigationSums %>%
  left_join(oroTotalsDF, by = "oro_type") %>%
  mutate(percent_articles = n_articles/total_coastEco*100)

adaptationSums <- adaptationSums %>%
  left_join(oroTotalsDF, by = "oro_type") %>%
  mutate(percent_articles = n_articles/total_coastEco*100)

# But also the percent may be low in comparison to all the articles out there for that ORO
# So also show the percentage that coastal ecosystem articles compose of total articles (coastEcoFraction)
oroTotalsDF_All <- predRel %>%
  inner_join(predType, by="analysis_id") %>%
  group_by(oro_type) %>%
  summarise(total_All = n_distinct(analysis_id))%>%
  collect() %>%
  mutate(oro_type = factor(oro_type, levels = typeAES$level, labels = typeAES$label)) 

mitigationSums <- mitigationSums %>%
  left_join(oroTotalsDF_All%>% select(oro_type, total_All), by = "oro_type") %>%
  mutate(percent_All = n_articles/total_All*100)
mitigationSums$coastEcoFraction = mitigationSums$total_coastEco/mitigationSums$total_All

adaptationSums <- adaptationSums %>%
  left_join(oroTotalsDF_All%>% select(oro_type, total_All), by = "oro_type") %>%
  mutate(percent_All = n_articles/total_All*100)
adaptationSums$coastEcoFraction = adaptationSums$total_coastEco/adaptationSums$total_All



## Format for a bivariate fill legend

library(biscale)

# Make my own bivariate palette
biPal5 <- c("#ffffff", "#d8f2f2", "#b0e5e5", "#86d7d7", "#5ac8c8", "#efd9ea", "#cacede", "#a5c3d2", "#7eb7c5", "#54aab8", "#dfb2d6", "#bda9cb", "#9aa0c0", "#7596b4", "#4f8ca8", "#cf8cc1", "#af85b7", "#8f7ead", "#6d76a3", "#496e97", "#be64ac", "#a15fa3", "#835a9a", "#645491", "#434e87")
palNames <- expand.grid(as.character(1:5), as.character(seq(1,5)))
palNames <- paste(palNames$Var1, palNames$Var2, sep="-")
names(biPal5) <- palNames
bi_pal(pal = biPal5, dim = 5) # Preview palette

# Make my own breaks 
library(classInt)
brks1 <- classIntervals(c(mitigationSums$percent_articles, adaptationSums$percent_articles),n=5, style = "kmeans")$brks
brks2 <- classIntervals(c(mitigationSums$coastEcoFraction, adaptationSums$coastEcoFraction), n=5,
                        style = "quantile")$brks
# cut data
mitigationSums$percent_articles_cut <- cut(mitigationSums$percent_articles, breaks = brks1, include.lowest = T)
adaptationSums$percent_articles_cut <- cut(adaptationSums$percent_articles, breaks = brks1, include.lowest = T)
mitigationSums$coastEcoFraction_cut <- cut(mitigationSums$coastEcoFraction, breaks = brks2, include.lowest = T)
adaptationSums$coastEcoFraction_cut <- cut(adaptationSums$coastEcoFraction, breaks = brks2, include.lowest = T)

# Format data frames for bivariate plotting
mitigationSums <- bi_class(mitigationSums, x=percent_articles_cut, y=coastEcoFraction_cut, dim=5, style = "equal")
adaptationSums <- bi_class(adaptationSums, x=percent_articles_cut, y=coastEcoFraction_cut, dim=5, style = "equal")

# calculate labels
labs <- bi_class_breaks(mitigationSums, x=percent_articles_cut, y = coastEcoFraction, style = "equal",
                dim = 5, dig_lab = 1, split = TRUE)



## For the adaptation plot, want to display two variables in triangles
# so format data for plotting
source(here::here("R/getTiles.R"))

humanDf <- getTiles(df = adaptationSums, filterVar = "adapt_to_threat", filterVal = "Human", 
                    orderVars = c(y="oro_type",x="ecosystem_type"),
                    tileLoc = "bottomright")
natureDf <- getTiles(df = adaptationSums, filterVar = "adapt_to_threat", filterVal = "Nature", 
                    orderVars = c(y="oro_type",x="ecosystem_type"),
                    tileLoc = "topleft"
                    )
cii_text <- data.frame(
  x=c(0.75,1.25),y=c(nrow(typeAES)+0.5,nrow(typeAES)-0.5),labs = c("Nature", "Human")
)
cii_text
```


```{r export sums to csv for reference}
write.csv(mitigationSums, here::here("outputs/coastalEcosystemsMitigationSums.csv"))
write.csv(adaptationSums, here::here("outputs/coastalEcosystemsAdaptationSums.csv"))
```


```{r plot panel C.i - Mitigation as a bivariate map}
fig4_C_i <- ggplot(mitigationSums, aes(y=oro_type, x=ecosystem_type))+
  geom_tile(aes(fill = bi_class), show.legend = FALSE)+
  bi_scale_fill(pal = biPal5, dim=5, na.value = "white")+
  #scale_fill_gradient2(mid="white",high="#3182bd", midpoint = 0, guide = guide_coloursteps())+
  #scale_y_discrete(limits=rev)+
  geom_hline(yintercept = c(0.5,2.5,4.5), col="black", linewidth=0.5)+
  # annotation_raster(marsh_ras, 0.5, 1.5, -2, -0)+
  # annotation_raster(mangrove_ras, 1.5, 2.5, -2, -0)+
  # annotation_raster(seagrass_ras, 2.5, 3.5, -2, -0)+
  # annotation_raster(coral_ras, 3.5, 4.5, -2, -0)+
  # coord_cartesian(ylim = c(-1.5, length(levels(mitigationSums$oro_type))), clip = 'off')+
  labs(
    #x = "Ecosystem type", #y = "ORO type", 
    title = "i. Mitigation"
  )+
  theme_bw()+
  theme(
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    legend.position = "bottom",
    #axis.text.x = element_text(angle=45, vjust=1, hjust=1)
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank()
  )



finalPlot <- ggdraw() +
  draw_plot(fig4_C_i, 0, 0, 1, 1) 
  #draw_plot(biLegend, 0, 0, 0.4, 0.4)


finalPlot
```


```{r plot panel C.ii - Adaptation as a bivariate map}

fig4_C_ii <- ggplot()+
  geom_polygon(data = humanDf, aes(x,y,group=id, fill = bi_class), show.legend = FALSE)+
  geom_polygon(data = natureDf, aes(x,y,group=id, fill = bi_class), show.legend = FALSE)+
  geom_text(data=cii_text, aes(x, y, label = labs), size=2)+
  
  bi_scale_fill(pal = biPal5, dim=5, na.value = "white")+
  
  geom_hline(yintercept = c(0.5,2.5,4.5), col="black", linewidth=0.5)+
  annotation_raster(marsh_ras, 0.5, 1.5, -2, -0)+
  annotation_raster(mangrove_ras, 1.5, 2.5, -2, -0)+
  annotation_raster(seagrass_ras, 2.5, 3.5, -2, -0)+
  annotation_raster(coral_ras, 3.5, 4.5, -2, -0)+
  
  # Format axes
  scale_x_continuous(breaks = 1:nrow(ecoTypeAES),labels = ecoTypeAES$label)+
  #scale_y_continuous(breaks = 1:nrow(typeAES),labels = typeAES$label)+
  scale_y_binned(breaks = 1:nrow(typeAES),labels = typeAES$label)+
  
  coord_cartesian(ylim = c(-1.5, nrow(typeAES)), clip = 'off')+
  labs(
    x = "Ecosystem type", #y = "ORO type", 
    title = "ii. Adaptation"
  )+
  theme_bw()+
  theme(
    #plot.margin = unit(c(0,0,0,0), "cm"),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    legend.position = "bottom",
    axis.text.x = element_text(angle=45, vjust=1, hjust=1)
    #axis.title.x = element_text(vjust = -8)
  )


finalPlot2 <- ggdraw() +
  draw_plot(fig4_C_ii, 0, 0, 1, 1) 
  #draw_plot(biLegend, 0, 0, 0.4, 0.4)


finalPlot2
```


```{r plot of legend}
labs2 <- labs
labs2$bi_x <- round(labs2$bi_x)
biLegend <- bi_legend(pal = biPal5,
                    dim = 5,
                    xlab = "% coastal ecosystem",
                    ylab = "% of all",
                    breaks = labs2,
                    arrows=FALSE,
                    size = 6)
biLegend
```

```{r combine two panel C subplots together}
fig4_C <- plot_grid(finalPlot, 
                    finalPlot2+draw_plot(biLegend, x=0, y=0, width=0.4, height=0.4),
                    nrow=2, rel_heights = c(0.7,1))
fig4_C
```

```{r old plot panel C.i - Mitigation}
fig4_C_i <- ggplot(mitigationSums, aes(y=oro_type, x=ecosystem_type))+
  geom_tile(aes(fill = percent_articles))+
  scale_fill_gradient2(mid="white",high="#3182bd", midpoint = 0, guide = guide_coloursteps())+
  scale_y_discrete(limits=rev)+
  geom_hline(yintercept = c(0.5,2.5,4.5), col="black", linewidth=0.5)+
  annotation_raster(marsh_ras, 0.5, 1.5, -2, -0)+
  annotation_raster(mangrove_ras, 1.5, 2.5, -2, -0)+
  annotation_raster(seagrass_ras, 2.5, 3.5, -2, -0)+
  annotation_raster(coral_ras, 3.5, 4.5, -2, -0)+
  #annotation_raster(macro_ras, 3.5, 4.5, -2, -0)+
  coord_cartesian(ylim = c(-1.5, length(levels(mitigationSums$oro_type))), clip = 'off')+
  labs(
    x = "Ecosystem type", #y = "ORO type", 
    fill = "%\ncoastal ecosystem\narticles",
    title = "i. Mitigation"
  )+
  theme_bw()+
  theme(
    #plot.margin = unit(c(0,0,0,0), "cm"),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    legend.position = "bottom",
    axis.text.x = element_text(angle=45, vjust=1, hjust=1)
    #axis.title.x = element_text(vjust = -8)
  )

fig4_C_i

```




# Write figure

```{r Write figure to pdf}
pdf(file = here::here("figures/main/marineSystemsAndClimateImpactDrivers.pdf"),
    width = 15, height = 7)
plot_grid(fig4_A_ggp,fig4_B_percent_ggp, fig4_C +theme(plot.margin = unit(c(2,0,0,0), "cm")), 
          rel_widths = c(1,1,1), ncol=3, labels = list("a.","b.","c."), label_size = 17)
while (!is.null(dev.list())) dev.off()

```

# Interpretation 
## Panel C

For socio-institutional and Built infrastructure and tech:
- salt marshes are associated with human and natural adaptation outcomes, but this signal is weak because they form a very small percentage of articles overall.

For conservation:
- small % of coastal ecosystem articles have mitigation outcomes, largest of these is found in mangroves (7%)
- Salt marshes and mangroves are most studied for human and natural adaptation outcomes, and coral reefs for natural adaptation but not human.

For HA Evolution:
- negligible numbers of articles with mitigation outcomes
- Most articles are focused on natural adaptation outcomes, with a high proportion for coral reefs. The latter also forms a high percent of all articles (68%)

Increase efficiency
- barely associated with coastal ecosystems 

For CO2 removal and storage:
- high proportion of articles with mitigation and natural adaptation outcomes are found in salt marsh, mangrove and (to a lesser extent) seagress ecosystems. These articles also form a high proportion of articles overall. 


Marine renewable energy:
- small proportion of articles associated with coastal ecosystems, but of these most are associated with salt marshes. This could just be an artefact of similar terms bewteen mitigation objectives?





